dispRity manual

### 2021-04-16 inst/gitbook/03_specific-tutorials.Rmd

Where *d* is the number of dimensions,
*n* the number of elements,
$\Gamma$ is the Gamma distribution,
$\lambda_i$ is the eigenvalue of each dimensions,
$\sigma^{2}$ is their variance and
$Centroid_{k}$ is their mean,
$Ancestor_{n}$ is the coordinates of the ancestor of element $n$,
$f(\mathbf{v}k)$ is function to select one value from the vector $\mathbf{v}$ of the dimension $k$ (e.g. it's maximum, minimum, mean, etc.),
*R* is the radius of the sphere or the product of the radii of each dimensions ($\displaystyle\prod_{i=1}^{k}R_{i}$ - for a hyper-ellipsoid),
$Reference_{k}$ is an arbitrary point's coordinates (usually 0),
\overrightarrow{b} is the vector defined by (`(point1, point2)`),
and \overrightarrow{i} is the vector defined by (`(point1, i)` where `i` is any row of the matrix).

@@

```{r}
## A generating a random tree with node labels
my_tree <- makeNodeLabel(rtree(5), prefix = "n")
## Adding the tip and node names to the matrix
dummy_space2 <- dummy_space[-1,]
rownames(dummy_space2) <- c(tree$tip.label, tree$node.label)

@@

## Measuring the disparity as the projection of each element
## on its root-ancestor vector
summary(dispRity(tree_space, metric = projections.tree,
                             phy    = dummy_tree,
                             type   = c("root", "ancestor")))
```

@@

```{r}
## A user defined function that's returns the centroid of
## the first three nodes
fun.root <- function(matrix, phy, row = NULL) {
  return(colMeans(matrix[phy$node.label[1:3], ]))
}
## Measuring the unscaled rejection from the vector from the
## centroid of the three first nodes
## to the coordinates of the first tip
summary(dispRity(tree_space, metric  = projections.tree,
                             phy     = dummy_tree,
                             measure = "distance",
                             type    = list(fun.root,
                                            tree_space[1, ])))
```

>>>>

Where *d* is the number of dimensions,
*n* the number of elements,
$\Gamma$ is the Gamma distribution,
$\lambda_i$ is the eigenvalue of each dimensions,
$\sigma^{2}$ is their variance and
$Centroid_{k}$ is their mean,
$Ancestor_{n}$ is the coordinates of the ancestor of element $n$,
$f(\mathbf{v}k)$ is function to select one value from the vector $\mathbf{v}$ of the dimension $k$ (e.g. it's maximum, minimum, mean, etc.),
*R* is the radius of the sphere or the product of the radii of each dimensions ($\displaystyle\prod_{i=1}^{k}R_{i}$ - for a hyper-ellipsoid),
$Reference_{k}$ is an arbitrary point's coordinates (usually 0),
$\overrightarrow{b}$ is the vector defined by (`(point1, point2)`),
and $\overrightarrow{i}$ is the vector defined by (`(point1, i)` where `i` is any row of the matrix).

@@

```{r}
## A generating a random tree with node labels
my_tree <- makeNodeLabel(rtree(5), prefix = "n")
## Adding the tip and node names to the matrix
dummy_space2 <- dummy_space[-1,]
rownames(dummy_space2) <- c(my_tree$tip.label,
                            my_tree$node.label)

@@

## Measuring the disparity as the projection of each element
## on its root-ancestor vector
summary(dispRity(tree_space, metric = projections.tree,
                             tree   = dummy_tree,
                             type   = c("root", "ancestor")))
```

@@

```{r}
## A user defined function that's returns the centroid of
## the first three nodes
fun.root <- function(matrix, tree, row = NULL) {
  return(colMeans(matrix[tree$node.label[1:3], ]))
}
## Measuring the unscaled rejection from the vector from the
## centroid of the three first nodes
## to the coordinates of the first tip
summary(dispRity(tree_space, metric  = projections.tree,
                             tree    = dummy_tree,
                             measure = "distance",
                             type    = list(fun.root,
                                            tree_space[1, ])))
```

### 2021-04-16 inst/gitbook/index.Rmd
Update index.Rmd

```{r, eval = TRUE, echo = FALSE}
## master version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/master/DESCRIPTION")
version_master <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_master <- 1.5

## release version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/release/DESCRIPTION")
version_release <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_release <- 1.5

## CRAN version
version_raw <- RCurl::getURL("https://cran.r-project.org/web/packages/dispRity/index.html")
version_CRAN <- strsplit(strsplit(version_raw, split = "\n<td>Version:</td>\n<td>")[[1]][2], split = "</td>\n</tr>\n<tr>\n<td>Depends:")[[1]][1]
version_CRAN <- 1.5
```

@@

Finally, this package is build on the shoulders of the whole open science philosophy so when bugs do occur and are caught by myself or the package users, they are quickly fixed and notified in the [`NEWS.md` file](https://github.com/TGuillerme/dispRity/blob/master/NEWS.md).

>>>>

```{r, eval = TRUE, echo = FALSE}
## master version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/master/DESCRIPTION")
version_master <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_master <- 1.6

## release version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/release/DESCRIPTION")
version_release <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_release <- 1.6

## CRAN version
version_raw <- RCurl::getURL("https://cran.r-project.org/web/packages/dispRity/index.html")
version_CRAN <- strsplit(strsplit(version_raw, split = "\n<td>Version:</td>\n<td>")[[1]][2], split = "</td>\n</tr>\n<tr>\n<td>Depends:")[[1]][1]
version_CRAN <- 1.6
```

@@

Finally, this package is build on the shoulders of the whole open science philosophy so when bugs do occur and are caught by myself or the package users, they are quickly fixed and notified in the [`NEWS.md` file](https://github.com/TGuillerme/dispRity/blob/master/NEWS.md). And all the changes to the package are [public and annotated](https://github.com/TGuillerme/dispRity/commits/master) so there's that too...
